### 2022-05-10 include/naive_rlpbwt.tex

\section{RLPBWT naive}
\subsection{Algoritmo per match massimali}