### 2022-05-10 include/panel_rlpbwt.tex

\section{RLPBWT con pannello denso}
\subsection{Algoritmo con matching statistics}