### 2022-05-10 include/phi.tex

\section{Funzione Phi}
\subsection{Costruzione della struttura di supporto}
\subsection{Estensione dei match}