### 2022-05-10 include/sviluppi.tex

\section{Sviluppi futuri}
\subsection{K-mems}
\subsection{RLPBWT multi-allelica}
\subsection{RLPBWT con dati mancanti}