### 2022-07-08 include/sviluppi.tex
fix

\section{Sviluppi futuri}
\paragraph{K-mems}
\paragraph{RLPBWT multi-allelica}
\paragraph{RLPBWT con dati mancanti}